BlogForever Crawler: Techniques and Algorithms\\to Harvest Modern Weblogs

### 2014-01-18 tex/1-intro.tex
Important reformulations

\TODO{
  After writing the first sentece, you should write what are our aims in this work. (keep it in the same paragraph).\\
  \\
  Our main objective in this work are to create better algorithms and techniques for blog content extraction. (maybe you want to write something extra here+++, then, continue with the contributions:\\
  \\
  Our contributions can be summarised as follows:
}

We present the BlogForever Crawler, a key component of the BlogForever platform \cite{kasioumis2013towards} responsible for traversing blogs, extracting their content and monitoring their updates. Our contributions can be summarized as follows:

@@

The rest of the paper is organized as follows. In Section 2, we present related work on web crawlers and web data extraction. In Section 3, we define our algorithms and in Section 4 we explain the techniques we used for implementation. We evaluate our algorithms and present results in Section 5. Finally, in Section 6 we present our conclusions and future work.

>>>>

We present the BlogForever Crawler, a key component of the BlogForever platform \cite{kasioumis2013towards} responsible for traversing blogs, extracting their content and monitoring their updates. Our main objective in this work is to design a crawler capable of extracting blog articles, authors, publication dates and comments. Our contributions can be summarized as follows:

@@

The rest of the paper is organized as follows. In \hyperref[algorithms]{Section~\ref*{algorithms}}  , we define our algorithms and in \hyperref[techniques]{Section~\ref*{architecture}}   we explain the techniques we used for implementation. We evaluate our algorithms and present results in \hyperref[evaluation]{Section~\ref*{evaluation}} . In \hyperref[relatedwork]{Section~\ref*{relatedwork}}  , we present related work on web crawlers and web data extraction. Finally, in \hyperref[conclusionandfuturework]{Section~\ref*{conclusionandfuturework}}  we present our conclusions and future work.

### 2014-01-18 tex/3-architecture.tex
Important reformulations

\section{Architecture}

\subsection{Scrapy and Invenio}
Introduce both projects with their respective strengths, tool/technology justification.

\subsection{JavaScript Rendering}
\begin{enumerate}
  \item PhantomJS
  \item "Show more comments" click
  \item Done upfront, every thing else is independent
\end{enumerate}

\subsection{Extraction Process}
High level overview: XPath build from RSS feeds

>>>>

\section{Architecture}
\label{architecture}

This section provides an overview of the crawler system architecture and the different techniques we used. The overall software architecture is presented and discussed, introducing the Scrapy framework and the enrichments we implemented for our specific usage. Then, we show how we integrated a headless web browser into the harvesting process to support blogs that use JavaScript to display page content. Finally, we talk about the design choices we made in view of a large scale deployment.

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Overview}

Our crawler is built on top of Scrapy \cite{scrapy2014}, an open-source Python framework for web crawling. Scrapy provides an elegant and modular architecture illustrated in \autoref{architecture}. Several components can be plugged into the Scrapy core infrastructure: \emph{Spiders}, \emph{Item Pipelines}, \emph{Downloader Middlewares} and \emph{Spider Middlewares}; each allowing us to implement a different type of functionality.

Our use case has two types of spiders: \emph{NewCrawl} and \emph{UpdateCrawl}, which implement the logic to respectively crawl a new blog and get updates from a previously crawled blog. After being downloaded and identified as blog posts (details in \autoref{enrichingscrapy}), pages are packed into \emph{Items} and sent through the following pipeline of operations:
\begin{enumerate}
  \item Render JavaScript
  \item Extract content
  \item Extract comments
  \item Download multimedia files
  \item Propagate resulting records to the back end
\end{enumerate}
This pipeline design provides great modularity. For example, disabling JavaScript rendering or plugging in an alternative back-end can be done by editing one single line of code.

\TODO{Write this properly...}
One of the main advantages of having full control over the crawling process is that contrarily to the general purpose crawlers, we do not to store all the web pages material. Instead, the content of interest is computed "on the fly", and directly saved into the back-end system. This propriety ...

\begin{figure}
  \capstart
  \centering
  \includegraphics[width=0.47\textwidth]{scrapy_architecture}
  \caption{Overview of the crawler architecture.\\(Credit: Pablo Hoffman, Daniel Graña, \cite{scrapy2014})}
  \label{architecture}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Enriching Scrapy}\label{enrichingscrapy}

In order to identify web pages as blog posts, our implementation enriches Scrapy with two components to narrow the extraction process down to the subsets of pages which are blog posts: \emph{blog post identification} and \emph{download priority heuristic}.

Given an URL entry point to a website, the default Scrapy behaviour traverses all the pages of the same domain in a \emph{last-in-first-out} manner. The \emph{blog post identification} function is able to identify whether a URL points to a blog post or not. Internally, for each blog, this function uses a regular expression constructed from the blog post URLs found in the web feed. This simple approach requires that blogs use the same URL pattern for all their posts (or false negatives will occur) which has to be distinct for pages that are not posts (or false positives will occur). In practice, this assumption holds for all blog platforms we encountered and seems to be a common practice amongst web developers.

In order to efficiently deal with blogs that have a large number of pages which are not posts, the \emph{blog post identification} mechanism is not sufficient. Indeed, after all pages identified as blog posts are processed, the crawler needs to download all other pages to search for additional blog posts. To replace the naive \emph{random walk}, \emph{depth first search} or \emph{breadth first search} web site traversals, we use a priority queue where priorities for new URLs are determined by a machine learning system. This mechanism has shown to be mandatory for blogs hosted on a single domain alongside large number of other types of web pages, such as those in forums or wikis.

The idea is to give high priority to URLs which are believed to point to pages with links to blog posts. These predictions are done using an active \emph{Distance-Weighted k-Nearest-Neighbour} classifier \cite{dudani1976}. Let $L(u)$ be the number of links to blog posts contained in a page with URL $u$. Whenever a page is downloaded, its URL $u$ and $L(u)$ are given to the machine learning system as training data. When the crawler encounters a new URL $v$, it will ask the machine learning system for a estimation of $L(v)$, and use this value as the download priority of $v$. $L(v)$ is estimated by calculating a weighted average of the values of the $k$ URLs most similar to $v$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{JavaScript rendering}

JavaScript is a widely used language for client-side scripting. While some applications simply use it for aesthetics, an increasing number of websites use JavaScript to download and display content. In such cases, traditional HTML based crawlers do not see web pages as they are presented to a human visitor by a web browser, and might therefore be obsolete for data extraction.

In our experiments whilst crawling the blogosphere, we encountered several blogs where crawled data was incomplete because of the lack of JavaScript interpretation. The most frequent cases were blogs using the Disqus \cite{disqus2014} and LiveFyre \cite{livefyre2014} comment hosting services. For webmasters, these tools are very handy because the entire comments infrastructure is externalized and their setup essentially comes down to including a JavaScript snippet in each target page. Both of these services heavily rely on JavaScript to download and display the comments, even providing functionalities such as real-time updates for edits and newly written comments. Less commonly, some blogs are fully rendered using JavaScript. When loading such websites, the web browser will not receive the page content as an HTML document, but will instead have to execute JavaScript code to download and display the page content. The Blogger platform provides the \emph{Dynamic Views} as a default template, which uses this mechanism \cite{antinharasymiv2011}.

To support blogs with JavaScript-generated content, we embed a full web browser into the crawler. After considering multiple options, we opted for PhantomJS \cite{phantomjs2014}, a headless web browser with great performance and scripting capabilities. The JavaScript rendering is the very first step of web page processing. Therefore, extracting blog post articles, comments or multimedia files works equally well on blogs with JavaScript-generated content and on traditional HTML-only blogs.

When the number of comments on a page exceeds a certain threshold, both Disqus and LiveFyre will only load the most recent ones and the stream of comments will end with a \emph{Show More Comments} button. As part of the page loading process, we instruct PhantomJS to repeatedly click on these buttons until all comments are loaded. Paths to Disqus and LiveFyre \emph{Show More} buttons are manually obtained. They constitute the only non-generic elements of our extraction stack which require human intervention to maintain and extend to other commenting platforms.

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Scalability}
When aiming to work with a large amount of input, it is crucial to build every layer of a system with scalability in mind \cite{thereactivemanifesto2013}. The BlogForever crawler, and in particular the two core procedures \emph{NewCrawl} and \emph{UpdateCrawl}, are designed to be usable as part of an event-driven, scalable and fault-resilient distributed system.

Heading in this direction, we made the key design choice to have both \emph{NewCrawl} and \emph{UpdateCrawl} as stateless components. From a high-level point of view, these two components are \emph{purely functional}:
%
\newcommand\URL{\mathbb{U}\text{RL}}
\newcommand\DATE{\mathbb{D}\text{ATE}}
\newcommand\RECORD{\mathbb{R}\text{ECORD}}
\begin{equation*}
  \begin{split}
    NewCrawl:    &~ \URL \rightarrow \mathcal{P}(\RECORD)\\
    UpdateCrawl: &~ \URL \times \DATE \rightarrow \mathcal{P}(\RECORD)
  \end{split}
\end{equation*}
%
where $\URL$, $\DATE$ and $\RECORD$ are respectively the set of all URLs, dates and records, and $\mathcal{P}$ designates the power set operator. By delegating all mutable state to the back end system, web crawler instances can be added, removed and used interchangeably.

### 2014-01-18 tex/4-evaluation.tex
Remove comments, do a pass UK of spell checker
Important reformulations

\section{Evaluation}\label{evaluation}

@@

% An extraction was considered successful when the returned string is a least 0.5 similar to the reference string, with respect to the Sørensen–Dice coefficient similarity.

@@

% running time eval, scalability with size of blogs
In addition to the quality of the extracted data we also evaluated the running time of the extraction procedure. The main point of interest is the ability of the extraction procedure to scale as the number of posts in the processed blog increases. This corresponds to the evaluation of a \emph{NewCrawl} task, which is in charge of harvesting all published content on a blog.

% the graph
\autoref{runningtime} shows the cumulated time spent for each article extraction procedure (this excludes common tasks such as downloading pages and storing results) as a function of the number of blog posts processed. We used the Quantum Diaries \cite{quantumdiaries} blog for this experiment.

% standard deviations
Data presented in this graph was obtained by taking the arithmetic mean over 10 measurements. These results are believed to be significant given that standard deviations are of the order of 2 milliseconds.

@@

\TODO{\\
  > what is the initial computation time? It would be good to know and have some numbers.\\\\
  The initial computations is the time we spend to go from 0 to 1 processed blog posts on the graph, which includes processing the web feed and the 15 pages it contains. I have the exact numbers in the repo but it's basically the tiny white space we see on the graph, ~1/8 second.
}

Past the initial computations, the cost of processing a blog post with our approach is almost zero. This is a consequence of having a blog-aware, rule-based algorithm. As already mentioned, the central idea is to first build extraction rules using the information provided by the web feed, and then use these rules on all posts of the blog. The initial increase in the curve of our approach corresponds to the computation of the extraction rules, which consists of processing the web feed and all the blog posts it references. Subsequent computations only involve parsing blog posts and applying extraction rules, which takes about 3 milliseconds and are barely visible on the scale of \autoref{runningtime}. The other evaluated solutions do not function this way: each blog post is processed as new and independent input, leading to approximately linear running times.

The vertical dashed line at 15 processed blog posts represents a suitable point of comparison of processing time per blog post as the test blog's web feed contains 15 blog posts. That being said, comparing raw performance of different algorithms implemented in different programming languages is not very informative given the high variations of running times observed across languages for identical algorithms \cite{hundt2011}.

% python x23 just-in-time compilation speed up http://dl.acm.org/citation.cfm?id=2069181

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsection{Preservation of blog visuals}
% \TODO{visuals/design/graphic/?}

% Additionally to the blog content extraction that we have been discussing so far, the BlogForever crawler is also responsible for capturing blog visuals. Indeed, one of the requirements of the BlogForever platform is to provide snapshots of blogs visuals in order to preserve changes in appearance \cite[FR53]{blogforeverrequirements2009}. Our final solution consists in using the embeded web browser to take screenshots after each page rendering. Before opting for this approach we considered 3 other solutions: GNU wget, wkhtmltopdf and OXPath. This subsection relates our evaluation of these tools for the specific purpose.

% \TODO{Is this whole subsection legitimate? It this part is not really relevant we could also simply not include it... I guess it is not a really useful from a research point of vue, but it might still be of some use for others to know what each of them can do. I think it's also important to say at some point how long it takes to render a pages, because if only look at the graph it seams like this is all super fast, but when we use PhantomJS the thing seriously slows down...}

% The first solution we considered was the GNU/Linux tool wget. With the appropriate options, wget can be used to download a webpage and the associated files (css, scripts and images). On simple webpages, this process effectively captures all files necessary to display the page locally. However, it falls short* to capture webpages that download content via javascript.

% Another solution we considered is wkhtmltopdf, a tool to produce pdf versions of web-pages. It uses the "print" function of it's embedded web browser to produce it's output and therefore supports all web technologies supported by it underling web browser.

% The OXPath project goes one step further by offering an extension of the XPath language to specify page interactions such as clicks and forms filling. It also make use of a complete web browser to render pages and execute page interactions sequentially. OXPath makes it simple to extract comments displayed across multiple pages or that requiring clicks to be loaded.

% \savevisualsTable

% intro, plan (why we pick these projects, what we want to show with this evaluation)

% \item "Wget crawl" http://blogforever.eu/blog/2011/05/21/creating-a-snapshot-of-a-blog-post-using-wget/
% \item wkhtmltopdf http://code.google.com/p/wkhtmltopdf/ http://blogforever.eu/blog/2011/05/17/rendering-and-storing-web-pages-using-wkhtmltopdf/
% \item OXPath
% \item Selenium + full browser

% table to recap

% discussion (ez of use vs power, fine because it's automated)

>>>>

\section{Evaluation}
\label{evaluation}

@@

@@

In addition to the quality of the extracted data we also evaluated the running time of the extraction procedure. The main point of interest is the ability of the extraction procedure to scale as the number of posts in the processed blog increases. This corresponds to the evaluation of a \emph{NewCrawl} task, which is in charge of harvesting all published content on a blog.

\autoref{runningtime} shows the cumulated time spent for each article extraction procedure (this excludes common tasks such as downloading pages and storing results) as a function of the number of blog posts processed. We used the Quantum Diaries \cite{quantumdiaries} blog for this experiment.

Data presented in this graph was obtained by taking the arithmetic mean over 10 measurements. These results are believed to be significant given that standard deviations are of the order of 2 milliseconds.

@@

As illustrated in \autoref{runningtime}, our approach spends the majority of it's total running time between the initialisation the processing of the first blog post. This initial increase of about 0.4 seconds corresponds to cost of executing \autoref{linearAlgo} to compute extraction rule for articles. As already mentioned, this consists in computing the \emph{best extraction rule} of each pages references by the web feed and picking the one functioning best on these pages. Once we have this extraction rule, processing subsequent blog posts only requires parsing and applying the rule, which takes about 3 milliseconds and are barely visible on the scale of \autoref{runningtime}. The other evaluated solutions do not function this way: each blog post is processed as new and independent input, leading to approximately linear running times.

The vertical dashed line at 15 processed blog posts represents a suitable point of comparison of processing time per blog post. Indeed, as the web feed of our test blog contains 15 blog posts, the extraction rule computation performed by our approach include the cost of entirely processing these 15 entries. That being said, comparing raw performance of algorithms implemented in different programming languages is not very informative given the high variations of running times observed across programming languages \cite{hundt2011}.

### 2014-01-18 tex/6-conclusion-and-future-work.tex
Important reformulations

\section{Conclusion and Future Work}

@@

Future work could investigate \emph{hybrid} extraction algorithms to try and achieve near 100\% success rates.

\TODO{\\
  > You didn't say anything about this in the evaluation, did you?
  Either present some numbers about it or remove this thing from the conclusions.
  \\\\
  I think I will simply rephrase it with less precisions, but the idea is that there is some overlap between the 7\% of posts we fail to extract and the 88.1\% of posts extracted by readability, likely in the order of 7\% * 88.1\% as the conditions of failure are completely independent.
}

Even if the overall performance of our approach is better than those of comparable projects (as shown in the evaluation), there are still a few cases where other techniques managed to extract data and we did not. This suggests that combining our approach with others such such as word density, tree edit distance matching or even spacial reasoning could lead to better performance.

>>>>

\section{Conclusion and Future Work}
\label{conclusionandfuturework}

@@

\Anotecontent{notimefordat}{\TODO{This might be necessary}: An in-depth analysis of causes of failure was not included in this paper given the high amount of manual work required to identify these causes on problematic pages.}

Future work could investigate \emph{hybrid} extraction algorithms to try and achieve near 100\% success rates. Indeed, we have observed\Anote{notimefordat} that the primary causes of failure of our approach were the insufficient quality of web feeds or the high structural variations of blog pages. This suggests that combining our approach with others techniques such as word density or spacial reasoning could lead to better performance given that these techniques are insensible to the above issues.
